Review: Adaptive Introgression Expanded the Genetic Base of Crops during post-Domestication Spread

### 2017-07-20 paper.tex
Update paper.tex

\subsection*{Basic:}
%We're beginning to see that introgression has occurred across a number of crops during their expansion.
%What is the genomic architecture of this introgression, and does the architecture suggest that it has been adaptive?
%At what geographic scale is introgression adaptive?  Is it very local?  Does one see different architectures of introgression across different regions?
%At what taxonomic scale does introgression occur?
%When do species become so diverged that introgression is either maladaptive or impossible?

@@

What is the genomic architecture of this introgression, and does the architecture suggest that it has been adaptive?
\gmj{Determination of adaptiveness could be accomplished genomically (looking for high LD regions that indicate selective sweeps) or by functional identification.}
%\gmj{Kinds of functional identification?  Knockout experiments, sequence homology with annotated genes, proximity to QTLs?}
After the hybrization events that lead to introgression, how long might the detectable genomic signals of introgression persist?
\gmj{Depends on number of generations, effective population size, mutation rate, recombination rate, patterns and strength of selection.}
\gmj{If an introgression from the progenitor sweeps across the cultivated species, how is it distinguished from a genomic region that is identical by descent and wasn't lost in the domestication process?}

At what taxonomic scale does introgression occur?
When do species become so diverged that introgression is either maladaptive or impossible (due to  Dobzhansky-Muller incompatiblities or other mechanisms)?
To what extent does the level of introgression across taxa depend on divergence time and/or mutation load between donor and recipient taxa? \gmj{I think we could include (effective) population size in this list of factors that determine extent of introgression.}
\gmj{I could also talk about cross-incompatibility factors in maize/teosinte hybridization vs. highly compatible asian rice and its relatives.  I probably wouldn't need a new source for the rice, but I might need to cite a paper about tcb1, ga1, and ga2.}

Does one see different architectures of introgression across different regions?
Have introgressed alleles been constrained to the population which initially recieved the introgression, or have those alleles spread to the rest of of the crop species?
Is introgression generally restricted to very local populations, or does it pervasive over broad geographic ranges?
At what geographic scale is introgression adaptive?
\gmj{Barley and maize most strongly show geographic patterns that we can talk about here, but I'm not sure how to discuss them again.}
To what extent does this depend on the slope of environmental gradients such as temperature, precipitation, and elevation across these ranges?
\gmj{Refer to the map and bar graph here?}

>>>>

\subsection*{Basic:}%We're beginning to see that introgression has occurred across a number of crops during their expansion.
%What is the genomic architecture of this introgression, and does the architecture suggest that it has been adaptive?
%At what geographic scale is introgression adaptive?  Is it very local?  Does one see different architectures of introgression across different regions?
%At what taxonomic scale does introgression occur?
%When do species become so diverged that introgression is either maladaptive or impossible?

@@

What is the genomic architecture of this introgression, and does the architecture suggest that it has been adaptive?
%Is introgression generally restricted to very local populations, or does it pervasive over broad geographic ranges?
At what geographic scale is introgression adaptive?
%\gmj{Barley and maize most strongly show geographic patterns that we can talk about here, but I'm not sure how to discuss them again.}
To what extent does this depend on the slope of environmental gradients such as temperature, precipitation, and elevation across these ranges?
%\gmj{Refer to the map and bar graph here?}
We can look at conservation of genomic architecture across landscapes and between populations, and make predictions about introgressions and their relations to local adaptation.
If the genomic architecture of an introgressed region is conserved across a broad ecogeographical region, this suggests that the introgression imparts adaptation to general environmental or climatic variables.
On the other hand, if the genomic architecture is conserved within populations but not between nearby populations in the region, this suggests that the introgressed regions offer adaptations to more local selective pressures.
If the genomic architecture of an introgressed region is not conserved within a population, there is little evidence that the introgression is adaptive.
%\gmj{Determination of adaptiveness could be accomplished genomically (looking for high LD regions that indicate selective sweeps) or by functional identification.}

After hybrization events that lead to introgression, how long might the detectable genomic signals of introgression persist?
%\gmj{Depends on number of generations, effective population size, mutation rate, recombination rate, patterns and strength of selection.}
%\gmj{If an introgression from the progenitor sweeps across the cultivated species, how is it distinguished from a genomic region that is identical by descent and wasn't lost in the domestication process?}
%Does one see different architectures of introgression across different regions?
%Have introgressed alleles been constrained to the population which initially recieved the introgression, or have those alleles spread to the rest of of the crop species?
Introgressed regions are easier to detect when there has been limited recombination to break them apart.
Therefore, introgressions are easiest to detect when they are either recent (few generations means few recombination events) or involve structural variation (which diminishes recombination rate).
Because recombination progressively breaks apart LD in introgressed regions, measurements of LD can be used to date introgression events (as in \cite{Poets2015}).

At what taxonomic scale does introgression occur?
When do species become so diverged that introgression is either maladaptive or impossible (due to  Dobzhansky-Muller incompatiblities or other mechanisms)?
Theory indicates that the most significant limiting factor to gene flow between progenitor and domesticate is divergence time.
Over time, diverged populations drift and become increasingly incompatible.
Small effective population size, and correspondingly high genetic load, of the introgressive population also limits gene flow.
Although perhaps less applicable in crop systems, this effect is seen in other well-documented cases of introgression (for example, Neanderthal introgression into humans, \cite{harris2016genetic}).
\gmj{I tracked down the sources that indicate that introgression is suppressed around genes.  The case example was Neanderthal alleles into humans, the paper titled "The genetic history of Ice Age Europe" \cite{fu2016genetic}, cited by the Graham Coop paper.  However, I'm unclear if this is a general rule, or simply a consequence of Neanderthal being high in deleterious genetic load.  Wouldn't crop systems, with wild relatives harboring putatively adaptive alleles with low load, show a different pattern?}
%To what extent does the level of introgression across taxa depend on divergence time and mutation load between donor and recipient taxa?
\gmj{I could also talk about cross-incompatibility factors in maize/teosinte hybridization vs. highly compatible asian rice and its relatives.  I probably wouldn't need a new source for the rice, but I might need to cite a paper about tcb1, ga1, and ga2.}
